simulation & inference of transients

### 2019-08-14 notebook/ghost-sims.Rmd
updated ghost sims

```{r}
p <- list(r = .05, K = 2, Q = 5, H = .38, sigma = .02, a=0.023, N = 4e3, x0 = 0.2, N = 1e4)
growth <- function(x, p) x * p$r * (1 - x / p$K)
consumption <- function(x, p) p$a * x ^ p$Q / (x^p$Q + p$H^p$Q)
```

@@

```{r}
det <- det_sim(may,p) 
det %>% ggplot(aes(t, x)) + geom_line() + theme_bw()
```

@@

```{r}
df %>% ggplot(aes(t, x, group=reps)) + 
  geom_line(alpha=0.1) +
  geom_line(data = det, color = "blue") + 
  geom_line(data = mean, color = "red")
```

@@

>>>>

```{r}
p <- list(r = .05, K = 2, Q = 5, H = .38, sigma = .02, a=0.023, N = 3e3, x0 = 0.2)
growth <- function(x, p) x * p$r * (1 - x / p$K)
consumption <- function(x, p) p$a * x ^ p$Q / (x^p$Q + p$H^p$Q)
```

@@

```{r}
det <- det_sim(may,p) 
det %>% ggplot(aes(t, x)) + geom_line() 
```

@@

## Stochastic ensemble mean vs deterministic mean

```{r}
df %>% ggplot(aes(t, x, group=reps)) + 
  geom_line(alpha=0.05) +
  geom_line(data = det, color = "blue") + 
  geom_line(data = mean, color = "red")
```

@@

## Deterministic system with initial conditions in neighborhood below ghost

```{r}
lambda <- function(x0, p){
                      pars <- p
                      p$x0 <- x0
                      det_sim(may, p)
                    }
mu <- 0.02
init <- mu + rnorm(100, 0, .02 * mu)
df <- future_map_dfr(init, lambda, p = p, .id = "reps")

df %>% ggplot(aes(t, x, group=reps)) + 
  geom_line(alpha=0.1)
```

## Deterministic System with initial condition in neighborhood of ghost

```{r}
mu <- 0.55
init <- mu + rnorm(100, 0, .02 * mu)
df <- future_map_dfr(init, lambda, p = p, .id = "reps")

df %>% ggplot(aes(t, x, group=reps)) + 
  geom_line(alpha=0.1)
```

```{r}
```
